1-generate-toys

### 2018-07-09 scripts/03-metric_characterisation/1old-generate_toys.Rmd
aaaaa! renaming scripts folders!

## Generate toy datasets for comparing scores
```{r}
source("analysis/analyses/3-metric_characterisation/generation.R")
source("analysis/analyses/3-metric_characterisation/perturbation.R")

experiment("3-metric_characterisation/1-generate_toys")
```

>>>>

## Generate toy datasets for comparing scores
```{r}
source("analysis/analyses/03-metric_characterisation/generation.R")
source("analysis/analyses/03-metric_characterisation/perturbation.R")

experiment("03-metric_characterisation/1-generate_toys")
```
